%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
 {Senior Software Engineer (Backend)} % Job Title
 {HungerStation (Delivery Hero)} % Organization
 {Dubai, UAE} % Location
 {Oct. 2023 - Present} % Date
 {
 \begin{cvitems}
 \item {Serving as a key member of the Integration Squad, responsible for building and maintaining critical communication channels between HungerStation's platform and external vendors, restaurant partners, and third-party service providers across Saudi Arabia.}
 \item {Designing and implementing scalable microservices that ensure seamless order flow and data synchronization between HungerStation's core platform and 50+ integrated restaurant chains and logistics providers.}
 \item {Developing compliance validation services to ensure all orders adhere to policies set by local government authorities, implementing automated checks and real-time monitoring systems.}
 \item {Optimizing GoLang-based backend services for high concurrency, reducing API response times by 35\% through efficient caching strategies, database query optimization, and connection pooling.}
 \item {Collaborating with product managers and cross-functional teams to define robust API contracts, implement comprehensive error handling, and establish service-level agreements (SLAs) for integration endpoints.}
 \item {Implementing observability solutions using Prometheus and Grafana, enabling proactive monitoring of integration health, performance metrics, and system reliability.}
 \item {Mentoring junior engineers through code reviews, pair programming sessions, and knowledge sharing, establishing best practices for microservices architecture and clean code principles.}
 \end{cvitems}
 }

 \vspace{4mm}

%---------------------------------------------------------
 \cventry
 {Sr. Software Engineer I} % Job Title
 {Careem (Uber Subsidiary)} % Organization
 {Lahore, Pakistan} % Location
 {Apr. 2022 - Sep. 2023} % Date(s)
 {
 \begin{cvitems}
 \item {Contributed to the Backend Supply Gate team within Careem's ride-hailing platform, working on critical services that manage driver supply, availability, and dispatch logic across the Middle East region.}
 \item {Developed and maintained services using diverse technology stacks including Laravel (PHP), Spring Boot (Java), and MEAN Stack (MongoDB, Express.js, Angular, Node.js), demonstrating versatility across different architectural patterns.}
 \item {Architected scalable backend solutions to handle millions of ride requests daily, implementing efficient algorithms for driver-rider matching, supply-demand balancing, and real-time location tracking.}
 \item {Optimized database queries and caching mechanisms to improve system performance, reducing response times for critical driver assignment operations by 40\%.}
 \item {Collaborated with mobile teams to design and implement RESTful APIs consumed by iOS and Android applications, ensuring robust error handling and comprehensive input validation.}
 \item {Participated in on-call rotation for production support, troubleshooting critical issues, and implementing fixes to maintain high availability for Careem's ride-hailing services.}
 \item {Contributed to architectural discussions and technical decision-making, evaluating trade-offs between different approaches and ensuring alignment with engineering best practices.}
 \end{cvitems}
 }

 \vspace{4mm}

%---------------------------------------------------------
 \cventry
 {Lead Software Engineer} % Job Title
 {LearnOBots} % Organization
 {Islamabad, Pakistan} % Location
 {Oct. 2018 - Mar. 2022} % Date(s)
 {
 \begin{cvitems}
 \item {Led engineering efforts at a pioneering EdTech startup specializing in STEAM (Science, Technology, Engineering, Arts, Mathematics) education, driving technical strategy and team development for multiple flagship products.}
 \item {\textbf{LearnOSTEAM Platform:} Architected and developed a comprehensive learning management system serving young students, integrating with multiple open-source educational tools and providing real-time progress tracking across 50+ schools and 10,000+ students.}
 \item {Built custom educational simulators and interactive learning modules, creating engaging experiences for students while maintaining detailed analytics on learning outcomes and student engagement.}
 \item {Implemented scalable backend infrastructure using Python Django, deployed on Kubernetes clusters with CI/CD pipelines via Jenkins, ensuring 99.9\% uptime during critical examination periods.}
 \item {Utilized Redis for session management and caching, AWS S3 for media storage, and designed microservices architecture to handle concurrent access from thousands of students.}
 \item {\textbf{POULTA - IoT Poultry Management System:} Designed and developed an innovative IoT-driven platform for the poultry industry, enabling farmers to digitize and optimize their operations through real-time monitoring and predictive analytics.}
 \item {Built comprehensive data capture system integrating manual entries with IoT sensor data from 500+ devices deployed across multiple farms, monitoring critical parameters including feed consumption, water intake, mortality rates, and environmental conditions.}
 \item {Developed predictive algorithms to detect abnormalities in flock behavior and health metrics, providing early warning alerts to farmers and enabling proactive intervention to prevent losses.}
 \item {Implemented full-stack solution using MEAN Stack (MongoDB, Express.js, Angular, Node.js), integrated with AWS IoT Core, AWS Greengrass for edge computing, AWS Lambda functions for serverless processing, and AWS SES/SNS for notifications.}
 \item {Programmed Arduino-based IoT devices using C++ to collect and transmit sensor data reliably, ensuring robust device-to-cloud connectivity even in challenging farm environments.}
 \item {Managed a team of 5 engineers, conducted code reviews, mentored junior developers, and established engineering processes including agile methodologies, version control workflows, and quality assurance practices.}
 \end{cvitems}
 }

 \vspace{4mm}

%---------------------------------------------------------
 \cventry
 {Sr. Software Engineer} % Job Title
 {Brainyloft (Remote)} % Organization
 {Philadelphia, USA (Remote)} % Location
 {Mar. 2018 - Sep. 2018} % Date(s)
 {
 \begin{cvitems}
 \item {Worked remotely for a Philadelphia-based tech startup, contributing to the development of innovative SaaS products for marketing automation and transportation management.}
 \item {\textbf{Volumefy - Instagram Marketing Tool:} Developed an automated Instagram growth platform designed to increase user followers through intelligent engagement strategies.}
 \item {Implemented automated commenting system with configurable patterns, auto-posting capabilities, and intelligent auto-unfollow features to optimize follower growth while maintaining platform compliance.}
 \item {Built scalable backend using custom PHP framework, integrated Python Scrapy for web scraping Instagram data, and utilized Selenium for browser automation to simulate organic user behavior.}
 \item {\textbf{TrackMyShuttle - Real-time Transit Tracking System:} Architected and developed a comprehensive shuttle tracking solution for transportation companies operating in New York City.}
 \item {Integrated GPS devices installed in shuttles to collect real-time location data, processed and displayed routes on Google Maps with accurate ETAs for all bus stops.}
 \item {Developed predictive analytics system using machine learning to forecast traffic patterns in New York City, providing drivers with proactive guidance about potential delays and optimal routing.}
 \item {Implemented real-time alert system to notify drivers and passengers about delays, route changes, and estimated arrival times, significantly improving service reliability and customer satisfaction.}
 \item {Designed scalable architecture to handle real-time data from 100+ shuttles simultaneously, ensuring low-latency updates and reliable system performance during peak hours.}
 \end{cvitems}
 }

 \vspace{4mm}

%---------------------------------------------------------
 \cventry
 {Sr. Software Engineer} % Job Title
 {HISDU - Punjab \& Sindh Healthcare Department} % Organization
 {Lahore, Pakistan} % Location
 {Jun. 2017 - Feb. 2018} % Date(s)
 {
 \begin{cvitems}
 \item {Worked with government healthcare department to develop mission-critical software systems for public hospitals across Punjab province, directly impacting healthcare delivery for millions of citizens.}
 \item {\textbf{MedicoLegal Certificate System:} Designed and developed a secure, centralized system for creating and managing Medical Legal Certificates (MLCs) across all government hospitals in the province.}
 \item {Implemented robust security measures and digital signatures to prevent certificate fabrication and ensure authenticity of medico-legal documentation, critical for law enforcement and judicial proceedings.}
 \item {Built real-time analytics dashboard providing provincial government with comprehensive insights into MLC statistics, trends, and patterns across all hospitals, enabling data-driven policy decisions.}
 \item {Developed using .NET MVC 5 framework with SQL Server database, implemented Redis caching for performance optimization, and ensured HIPAA-compliant data security measures.}
 \item {\textbf{Electronic Medical Record (EMR) System:} Architected and developed a comprehensive EMR solution for Tehsil and District healthcare units, digitizing patient records and clinical workflows.}
 \item {Implemented features for doctors to access complete patient medical history, request and review lab reports, track prescriptions, and maintain continuity of care across multiple visits and healthcare facilities.}
 \item {Developed companion Android application enabling mobile access to patient records, allowing healthcare providers to review critical information at point of care.}
 \item {Built modern web interface using Angular framework, backend APIs using .NET Core, and implemented role-based access control to ensure appropriate data access for different healthcare staff levels.}
 \item {Collaborated with healthcare professionals, hospital administrators, and government officials to gather requirements, conduct user training, and ensure successful system adoption across 50+ healthcare facilities.}
 \end{cvitems}
 }

 \vspace{4mm}

%---------------------------------------------------------
 \cventry
 {Web Developer} % Job Title
 {TechLeadz} % Organization
 {Lahore, Pakistan} % Location
 {Nov. 2016 - May 2017} % Date(s)
 {
 \begin{cvitems}
 \item {Worked at a service-based software house delivering custom web applications for diverse clients across multiple industries and technology stacks.}
 \item {\textbf{TravelLinked - Travel Agency Platform:} Developed multiple modules for a comprehensive travel agency management system built in Laravel framework.}
 \item {Implemented features for booking management, customer relationship management, itinerary planning, payment processing, and automated email notifications for travel confirmations.}
 \item {Gained exposure to diverse technology stacks including ColdFusion (legacy system maintenance), Laravel (modern PHP framework), and Angular (frontend development), working on various client projects simultaneously.}
 \item {Collaborated with project managers and clients to gather requirements, provide technical estimates, and deliver solutions within tight deadlines while maintaining code quality standards.}
 \item {Participated in code reviews, learned industry best practices for web development, and established foundation for full-stack development skills across multiple technologies.}
 \end{cvitems}
 }

%---------------------------------------------------------
\end{cventries}
